\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-07-01 paper.tex
Update on Overleaf.

  %%% Relations between components
  \path (shary.340) edge [->, bend left] node[label] {motion plan \\ requests} (mhp);
  \path (shary.west) edge [<->, bend right] node[label] {shared \\ plans} (hatp);
  \path (hatp) edge [<-, bend right] node[label] {world model and \\ agents beliefs} (oro.170);
  \path (dialogs) edge [<->, bend left] node[label] {natural language \\ grounding} (oro.190);
  \path (spark.100) edge [->, bend right] node[label] {symbolic \\ facts} (oro);
  \path (spark.5) edge [->, bend right] node[label] {environment\\model} (mhp);
  \path (shary) edge [<->, bend left] node[label] {events, \\ world model and \\ agents beliefs} (oro);
  \path (shary) edge [<->, bend left] node[label] {action monitoring \\ and management of \\ position hypotheses} (spark);
  \path (lowlevel) edge [->] (spark);
  \path (lowlevel.east) edge [<-, bend right=80, looseness=1.2] node[label] {atomic\\actions} (shary.east);

@@

Monitoring human activity is needed by the execution controllers to track the
engagement of the human and the progress of her actions and also to synchronise seamlessly
its own actions with the human actions. Full human action
and activity recognition is a task that requires knowledge and reasoning both on
high-level facts like goals, intentions and plans, as well as bottom-up data
from human and object motions. {\sc Spark} implements a set of simple temporal and
geometric heuristics on human hand trajectories and possible objects placements
to recognise simple atomic actions. Those primitive actions are assessed through
monitoring situations like ``an empty hand is close to an object on a table''
(precursor for a \emph{pick}), or ``a hand holding an object is over a
container'' (precursor for a \emph{throw}).  {\sc Spark} recognises a set of
such primitives. When combined with the other geometric computations and a predictive
plan of the human actions (see Section~\ref{hatp}), the execution controller can
track the fulfilment of the pre- and post-conditions of the predicted human
actions. As a result, the robot can monitor the engagement of the human and the
overall progress of the human-robot shared plan.

@@

Like most robotic architectures, actions are split into \emph{atomic actions}
that are combined into \emph{tasks}. Tasks are created either statically or dynamically.
The {\sc pyRobots} controller, for instance, statically combines the actions listed in
table~\ref{table|pyrobots_actions} to implement the high-level tasks it exposes: {\tt
lookAt}, {\tt moveTo}, {\tt getFromHuman}, {\tt showObject}, {\tt giveObject},
{\tt pickObject}, {\tt bringObject}, {\tt putObject}, {\tt hideObject}.
Our other controller, {\sc Shary}, relies on the symbolic task planner to
dynamically generate, at run-time, suitable sequence of atomic actions.

@@

The first task (\concept{TAKE(GREY\_TAPE, TABLE)}) is instantiated by checking
that the task pre-conditions hold (in particular, \stmt{GREY\_TAPE isOn TABLE}
must be true), and calling the 3D motion planner (column \emph{Actions},
left). The motion planner returns two atomic actions ({\tt PICK\_GOTO} followed
by {\tt TAKE\_TO\_FREE}) that the controller executes (by first reaching for
the object, grasping it and bringing it back to a free position).  The robot's
perception monitors the evolution of the scene until the task's post-conditions
are verified (at $t_2$, by satisfying the statement \stmt{ROBOT hasInHand
TAPE}), and the next task is then started (placing the tape so that it becomes
reachable by the human).

@@

Robotics is traditionally regarded as the prototypical instance of
\emph{embodied} artificial intelligence, and this dimension is especially
prevalent in human-robot interaction, where agents have to share and
collaborate in a joint physical environment.  This leads to a tight coupling
between the symbolic and the geometric realms: while AI at its origins was
mostly concerned with symbolic models, it has been since recognised that not
only the mind is not a purely abstract system, disconnected from the physical
world, but even more, cognition fundamentally relies on its relation to the
physical world (so-called \emph{embodied cognition}). Varela~\cite{Varela1992}
is one of the main discoverers of these mechanisms, and coined the concept of
\emph{enactivism} as the theoretical framework that studies the links between
cognition, embodiment and actions.  This has since been thoroughly studied in
robotics and artificial intelligence (Pfeifer and
Bongard~\cite{pfeifer2007body} is one of the reference).

@@

We have presented in this paper a large deliberative architecture designed for
social robots. While most of its sub-components have been independently
presented in other publications, we offer here for the first time a perspective
on the model of integration of these components into a coherent and consistent
system for social human-robot interaction. We have first exposed our underlying
knowledge model based on Description Logics~\cite{Lemaignan2010} and some of the
resulting reasoning capabilities pertaining to disambiguation~\cite{Ros2010b}
and mental modelling~\cite{warnier2012when} that are shown to effectively
scaffold interaction using human-level semantics and cognitive skills. We have
then presented our approach to symbol grounding, build on an amodal situation
assessment environment~\cite{Sisbot2011} that supports perspective
taking~\cite{Marin2008,Ros2010}. We combine it further with a situated natural
language processor~\cite{Lemaignan2011a} to provide complete multi-modal
interactive communication.  The paper also covers our symbolic social task
planner~\cite{Alili2008, Alili2009, Lallement2014}: it generates predictive
plans of the human actions that enable the system to plan for joint human-robot
tasks. It can also make use of social heuristics to optimise plans for social
acceptability. We briefly mention our human-aware motion and manipulation
planner~\cite{Sisbot2007,Sisbot2008,Mainprice2011,Pandey2011,sisbot2012human,kruse2013human}, and finally present two
execution controller, the PRS-based {\sc
Shary}~\cite{clodic2009,fiore2014,clodic2014key}
and the event-driven {\sc pyRobots}~\cite{lemaignan2015pyrobots}.

@@

Human-Robot Interaction is and is going to remain a challenging field for
Artificial Intelligence. We hope that this contribution helps with clarifying
some of these challenges.

@@

This work has been partially supported by EU FP7 ``SAPHARI'' (grant ICT-287513),
and the EU H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).

>>>>

  %%% Relations between components
  \path (shary.340) edge [->, bend left] node[label] {motion plan \\ requests} (mhp);
  \path (shary.west) edge [<->, bend right] node[label] {shared \\ plans} (hatp);
  \path (hatp) edge [<-, bend right] node[label] {world model and \\ agents beliefs} (oro.170);
  \path (dialogs) edge [<->, bend left] node[label] {natural language \\ grounding} (oro.190);
  \path (spark.100) edge [->, bend right] node[label] {symbolic \\ facts} (oro);
  \path (spark.5) edge [->, bend right] node[label] {environment\\model} (mhp);
  \path (shary) edge [<->, bend left] node[label] {events, \\ world model and \\ agents beliefs} (oro);
  \path (shary) edge [<->, bend left] node[label] {action monitoring \\ and management of \\ position hypotheses} (spark);
  \path (lowlevel) edge [->] (spark);
  \path (lowlevel.east) edge [<-, bend right=80, looseness=1.2] node[label] {elementary\\actions} (shary.east);

@@

Monitoring human activity is needed by the execution controllers to track the
engagement of the human and the progress of her actions and also to synchronise seamlessly
its own actions with the human actions. Full human action
and activity recognition is a task that requires knowledge and reasoning both on
high-level facts like goals, intentions and plans, as well as bottom-up data
from human and object motions. {\sc Spark} implements a set of simple temporal and
geometric heuristics on human hand trajectories and possible objects placements
to recognise simple elemntary actions. Those primitive actions are assessed through
monitoring situations like ``an empty hand is close to an object on a table''
(precursor for a \emph{pick}), or ``a hand holding an object is over a
container'' (precursor for a \emph{throw}).  {\sc Spark} recognises a set of
such primitives. When combined with the other geometric computations and a predictive
plan of the human actions (see Section~\ref{hatp}), the execution controller can
track the fulfilment of the pre- and post-conditions of the predicted human
actions. As a result, the robot can monitor the engagement of the human and the
overall progress of the human-robot shared plan.

@@

Like most robotic architectures, actions are split into \emph{elementary actions}
that are combined into \emph{tasks}. Tasks are created either statically or dynamically.
The {\sc pyRobots} controller, for instance, statically combines the actions listed in
table~\ref{table|pyrobots_actions} to implement the high-level tasks it exposes: {\tt
lookAt}, {\tt moveTo}, {\tt getFromHuman}, {\tt showObject}, {\tt giveObject},
{\tt pickObject}, {\tt bringObject}, {\tt putObject}, {\tt hideObject}.
Our other controller, {\sc Shary}, relies on the symbolic task planner to
dynamically generate, at run-time, suitable sequence of elementary actions.

@@

The first task (\concept{TAKE(GREY\_TAPE, TABLE)}) is instantiated by checking
that the task pre-conditions hold (in particular, \stmt{GREY\_TAPE isOn TABLE}
must be true), and calling the 3D motion planner (column \emph{Actions},
left). The motion planner returns two elementary actions ({\tt PICK\_GOTO} followed
by {\tt TAKE\_TO\_FREE}) that the controller executes (by first reaching for
the object, grasping it and bringing it back to a free position).  The robot's
perception monitors the evolution of the scene until the task's post-conditions
are verified (at $t_2$, by satisfying the statement \stmt{ROBOT hasInHand
TAPE}), and the next task is then started (placing the tape so that it becomes
reachable by the human).

@@

Robotics is traditionally regarded as the prototypical instance of
\emph{embodied} artificial intelligence, and this dimension is especially
prevalent in human-robot interaction, where the robot has to share and
collaborate in a joint physical environment.  This leads to a tight coupling
between the symbolic and the geometric realms: while AI at its origins was
mostly concerned with symbolic models, it has been since recognised that not
only the mind is not a purely abstract system, disconnected from the physical
world, but even more, cognition fundamentally relies on its relation to the
physical world (so-called \emph{embodied cognition}). Varela~\cite{Varela1992}
is one of the main discoverers of these mechanisms, and coined the concept of
\emph{enactivism} as the theoretical framework that studies the links between
cognition, embodiment and actions.  This has since been thoroughly studied in
robotics and artificial intelligence (Pfeifer and
Bongard~\cite{pfeifer2007body} is one of the reference).

@@

We have presented in this paper an instance of a complete deliberative architecture designed for
social robots. While most of its sub-components have been independently
presented in other publications, we offer here for the first time a perspective
on the model of integration of these components into a coherent and consistent
system for social human-robot interaction. We have first exposed our underlying
knowledge model based on Description Logics~\cite{Lemaignan2010} and some of the
resulting reasoning capabilities pertaining to disambiguation~\cite{Ros2010b}
and mental modelling~\cite{warnier2012when} that are shown to effectively
scaffold interaction using human-level semantics and cognitive skills. We have
then presented our approach to symbol grounding, build on an amodal situation
assessment environment~\cite{Sisbot2011} that supports perspective
taking~\cite{Marin2008,Ros2010}. We combine it further with a situated natural
language processor~\cite{Lemaignan2011a} to provide complete multi-modal
interactive communication.  The paper also covers our symbolic social task
planner~\cite{Alili2008, Alili2009, Lallement2014}: it generates predictive
plans of the human actions that enable the system to plan for joint human-robot
tasks. It can also make use of social heuristics to optimise plans for social
acceptability. We briefly mention our human-aware motion and manipulation
planner~\cite{Sisbot2007,Sisbot2008,Mainprice2011,Pandey2011,sisbot2012human,kruse2013human}, and finally present two
execution controller, the PRS-based {\sc
Shary}~\cite{clodic2009,fiore2014,clodic2014key}
and the event-driven {\sc pyRobots}~\cite{lemaignan2015pyrobots}.

@@

Human-Robot Interaction is and is going to remain a challenging field for
Artificial Intelligence. We hope that this contribution helps with clarifying
of these challenges and making them concrete decisional problems.

@@

This work has been partially supported by EU FP7 "CHRIS" (grant 215805) and ``SAPHARI'' (grant ICT-287513) projects, and the EU H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).
